analysis-pilot

### 2023-08-16 code/analysis-pilot.Rmd
new
15:26

#so like a third mismatch, and only a couple off by more than 1
```
# Prep accuracy

>>>>

#so like a third mismatch, and only a couple off by more than 1
```
# timed_transcripts editing:
```{r}
timed_new <- timed_transcripts %>% 
  filter(!speaker %in% c("I", "M", "i")) %>% 
  mutate(wordCount = str_count(text, "\\S+"))

# filter trials, filter out practice trials, round trialNumStart up for 0.5
# geom line - color = game OR group = game

# Prep accuracy
